Generating urban morphologies at large scales

### 2019-03-14 paper.tex
.

\begin{abstract}
% Abstract length should not exceed 250 words
  At large scales, typologies of urban form and corresponding generating processes remain an open question with important implications regarding urban planning policies and sustainability. We propose in this paper to generate urban configuration with morphogenesis models, and compare these to real configurations according to morphological indicators.
\end{abstract}

@@

% - no unified definition of urban form
% - neither single model of morphogenesis / indicators to measure forms

% some word on procedural modeling ?
% Watson, B., Müller, P., Veryovka, O., Fuller, A., Wonka, P., & Sexton, C. (2008). Procedural urban modeling in practice. IEEE Computer Graphics and Applications, 28(3), 18-26.
% mostly focused on graphics, 3D etc (not generative processes themselves)

@@

\cite{herold2003spatiotemporal} measures at the scale of land-use patch (CA model - calibration of SLEUTH ; ``mesoscopic'')

The approach developed here is similar to the one taken by \cite{raimbault2018calibration} but at a much larger scale.

>>>>

\begin{abstract}
% Abstract length should not exceed 250 words
  At large scales, typologies of urban form and corresponding generating processes remain an open question with important implications regarding urban planning policies and sustainability. We propose in this paper to generate urban configurations at large scales, typically of districts, with morphogenesis models, and compare these to real configurations according to morphological indicators. Real values are computed on a large sample of districts taken in European urban areas. We calibrate each model and show their complementarity to approach the variety of real urban configurations, paving the way to multi-model approaches of urban morphogenesis.
\end{abstract}

@@

The study of forms of the built environment, and more precisely of the urban environment, has been the subject of different disciplines such as architecture, urban planning, or geography, with different approaches corresponding to various scales and processes \citep{moudon1997urban}. Establishing typologies of urban morphologies, and understanding their link with underlying urban growth processes, is nowadays a crucial issue for sustainability as a large majority of the world population live in cities and energy consumption is closely related to urban form \citep{newman2000sustainable}.

Although there is neither a unified definition of urban form, nor unified generative models and quantitative indicators to measure it, several approaches are close to the spirit of artificial life and generative social science. Procedural modeling \citep{watson2008procedural} aims at generating realistic cities, but is mostly focused on the visual impression given and does not consider realistic generative processes. It is furthermore developed largely at larger scales than the one of the district \citep{}. Approaches linked to urban planning have focused on the spatial distribution of land-use, at multiple scales \citep{}, and proposed cellular automata models for urban sprawl, generally at the scale of the metropolitan area \cite{herold2003spatiotemporal}.

@@

This paper proposes a first step towards a systematic understanding of generative models of the urban form, at a large scale. The approach taken here is similar to the one taken by \cite{raimbault2018calibration}, which computes urban form indicators at a mesoscopic scale (metropolitan area) and calibrates a reaction-diffusion morphogenesis model. We consider real urban configurations at the scale of the district (fixed spatial window of 500m), compute their morphological characteristics, and use these measures to calibrate different generative models of urban layouts at the same scale. Our contribution is twofold: (i) we synthesize a set of indicators relevant at this scale, and compute them on a large sample of real urban configurations in European urban areas; (ii) we provide three different generative models

The rest
